\mythesistitleNOTSYNPOSIS \tnote[fyi]{Synopsis title is ``Generalization of Consecutive Ones Property of Binary Matrices''}

### 2012-01-27 src/010chap1.tex
See diff please can't recall.

\begin{table}[b] %[htbp]
  \centering
  {\footnotesize    
    \begin{tabular}{l||l}
      \begin{tabular}{rcl}
        $T $&$=$&$ \text{\em Street map tree of \residenceblock}$\\
        $V(T) $&$=$&$ \{ 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11 \}$\\
        $\cP $&$=$&$ \{R\xLLL, R\xGGG, R\xBBB, R\xTTT\}$\\
        $R\xLLL $&$=$&$ \{9, 1, 5, 3, 11\}$\\
        $R\xGGG $&$=$&$ \{7, 2, 6, 5\}$\\
        $R\xBBB $&$=$&$ \{8, 2, 4 \}$\\
        $R\xTTT $&$=$&$ \{10, 6, 5, 3\}$\\
        $n $&$=$&$ |V| = 11$\\
        $m $&$=$&$ |\cP| = 4$\\\\
        $\cl $&$=$& {\em Study group to route mapping}\\        
        $\cl(\mathbb{X}) $&$=$&  $R\mathbb{X}$ for all $\mathbb{X} \in
        \cF$
      \end{tabular} & 
      \begin{tabular}{c}
        {\em Apartment allocation }($\phi$)\\
        \begin{tabular}{c|c}                      
          1  & \xSa\\
          2  & \xPi\\
          3  & \xFr\\
          4  & \xWo\\
          5  & \xCh\\
          6  & \xVi\\
          7  & \xPa\\
          8  & \xSn\\
          9  & \xLu\\
          10 & \xLi\\
          11 & \xSc                     
        \end{tabular}
      \end{tabular}\\
    \end{tabular}
  }
  \caption{\figtabsize A solution to \illustrationproblem} %study group accommodation problem
  \label{tab:iltree}
\end{table}

@@

\section{Basic preliminaries - general definitions and nomenclature}
\label{sec:basicprelim}

@@

\section{Consecutive-ones Property Testing - a Brief Survey}
\label{sec:background}

@@

\section{Application of COP in Areas of Graph Theory and
  Algorithms}
\label{sec:appcopGTA}

\temptext{Combine COP in Relational Database Model + COP in Graph
  Isomorphism + Certifying Algorithms}

%\subsection{COP in Relational Database Model}
\label{sec:apprdbm}
\tnote{(set systems theme)}

%\subsection{}
\label{sec:appgraphiso}
\tnote{(canonization theme)}

%\subsection{}
\label{sec:appcertalgo}
\tnote{ (certification McC04 theme)}

\section{Generalization of COP - the Motivation}
\label{sec:motive}
Section~\ref{sec:copmatrices} introduced a succinct characterization
for consecutive-ones property which is solely based on the cardinality
properties of the set representations of the matrix's columns
\cite{nsnrs09}. This result is very relevant to this thesis because
aside from it simplifying COT to a great degree, our generalization
problem is motivated by their results.

@@

\section{Summary of New Results in this Thesis}
\label{sec:results}

>>>>

\begin{table}[b] %[htbp]
  \centering
  {\footnotesize    
    \begin{tabular}{l||l}
      \begin{tabular}{rcl}
        $T $&$=$&$ \text{\em Street map tree of \residenceblock}$\\
        $V(T) $&$=$&$ \{ 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11 \}$\\
        $\cP $&$=$&$ \{R\xLLL, R\xGGG, R\xBBB, R\xTTT\}$\\
        $R\xLLL $&$=$&$ \{9, 1, 5, 3, 11\}$\\
        $R\xGGG $&$=$&$ \{7, 2, 6, 5\}$\\
        $R\xBBB $&$=$&$ \{8, 2, 4 \}$\\
        $R\xTTT $&$=$&$ \{10, 6, 5, 3\}$\\
        $n $&$=$&$ |V| = 11$\\
        $m $&$=$&$ |\cP| = 4$\\\\
        $\cl $&$=$& {\em Study group to route mapping}\\        
        $\cl(\mathbb{X}) $&$=$&  $R\mathbb{X}$ for all $\mathbb{X} \in
        \cF$
      \end{tabular} & 
      \begin{tabular}{c}
        {\em Apartment allocation }($\phi$)\\
        \begin{tabular}{c|c}                      
          1  & \xSa\\
          2  & \xPi\\
          3  & \xFr\\
          4  & \xWo\\
          5  & \xCh\\
          6  & \xVi\\
          7  & \xPa\\
          8  & \xSn\\
          9  & \xLu\\
          10 & \xLi\\
          11 & \xSc                     
        \end{tabular}
      \end{tabular}\\
    \end{tabular}
  }
  \caption{\figtabsize A solution to \illustrationproblem}
  \label{tab:iltree}
\end{table}

@@

\section[Basic preliminaries]{Basic preliminaries} 
\label{sec:basicprelim}

@@

\section[Brief Survey]{Consecutive-ones Property - a Brief Survey}
\label{sec:background}

@@

% \section[Some applications of \COP]{Application of COP in Areas of Graph Theory and
%   Algorithms}
% \label{sec:appcopGTA}

% \temptext{Combine COP in Relational Database Model + COP in Graph
%   Isomorphism + Certifying Algorithms}

% %\subsection{COP in Relational Database Model}
% \label{sec:apprdbm}
% \tnote{(set systems theme)}

% %\subsection{}
% \label{sec:appgraphiso}
% \tnote{(canonization theme)}

% %\subsection{}
% \label{sec:appcertalgo}
% \tnote{ (certification McC04 theme)}

\section[Generalization of COP]{Generalization of COP - the Motivation}
\label{sec:motive}
Section~\ref{sec:copmatrices} introduced a succinct characterization
for consecutive-ones property which is solely based on the cardinality
properties of the set representations of the matrix's columns
\cite{nsnrs09}. This result is very relevant to this thesis because
aside from it simplifying COT to a great degree, our generalization
problem is motivated by their results.

@@

\section[Summary of new results]{Summary of New Results in this Thesis}
\label{sec:results}

### 2012-01-27 src/020chap2.tex
See diff please can't recall.

%\chapter{\CoP\,-- A Survey of Important Results}
\chapter[Consecutive-ones Property -- A Survey]{Consecutive-ones Property -- A Survey of Important Results}
\label{ch:copsurvey}

@@

\subsection{Booth and Lueker's $PQ$ tree -- a linear COT algorithm}

@@

\section{COP in Graph Isomorphism}
\label{sec:surveygraphiso}
\tnote{Expand on sec:appgraphiso} \tnote{(canonization theme)}

>>>>

%\chapter{\CoP\,-- A Survey of Important Results}
\chapter[COP -- A Survey]{Consecutive-ones Property -- A Survey of
  Important Results} 
\label{ch:copsurvey}

@@

\subsection{Booth and Lueker's $PQ$-tree -- a linear COT algorithm} %[\PQtree]

@@

\section{COP in Graph Isomorphism}
\label{sec:surveygraphiso}
\tnote{(canonization theme)}

### 2012-01-27 src/030chap3.tex
Did some over all clean up. Added fancy chapter headings. Begun work on opt survey.
See diff please can't recall.

\chapter{Tree Path Labeling of Path Hypergraphs - the New Results}
\label{ch:myresearch}

@@

\section{Summary of Proposed Problems}
\label{sec:myresearchintro}
In Section~\ref{sec:motive} we see that consecutive-ones property and
its equivalent problem of interval labeling of a hypergraph is a
special case of the general problem of tree path labeling of path
hypergraphs.  The problem of consecutive-ones property testing can be
easily seen as a simple constraint satisfaction problem involving a
hypergraph or a system of sets from a universe. Every column (row) of
the binary matrix can be converted into a set of non-negative integers
which are the indices of the rows (columns) with {\un}s in that column
(row). When observed in this context, if the matrix has the COP on
columns (rows), a reordering of its rows (columns) will result in sets
that have only consecutive integers. In other words, the sets after
applying the COP row (column) permutation are intervals.  In this
form, one can see that this is indeed the problem of finding interval
assignments to the given set system \cite{nsnrs09} with a single
permutation of the universe (set of row or column indices for COP of
columns or rows, respectively) which permutes each set to an
interval. The result in \cite{nsnrs09} characterizes interval
assignments to the sets which can be obtained from a single
permutation of the universe. The cardinality of the interval
assigned to it must be same as the cardinality of the set, and the
intersection cardinality of any two sets must be same as the
intersection cardinality of the corresponding intervals. This is a
necessary and sufficient condition. \tnote{(ICPIA) put reference to
  survey chapter}

@@

\section{Preliminaries to new results}
\label{ch:prelims}

@@

\section{Characterization of Feasible Tree Path Labeling}
\label{sec:feasible}

@@

\section{ Computing feasible TPL with special target trees}
\label{sec:spltargettree}

@@

\section{Complexity of Tree Path Assignment-A Discussion}
\label{complexity}
Recall that the input to the Tree Path Assignment question is an order
pair $(\cF,T)$ where $\cF$ is a family of subsets of an universe $U$,
and $T$ is a tree such that $|V(T)| = |U|$.  The question is to come
up with a bijection from $U$ to $V(T)$ such that the image of each set
in $\cF$ is a path in $T$.

>>>>

\chapter[Tree Path Labeling]{Tree Path Labeling of Path
  Hypergraphs -- New Results}
\label{ch:myresearch}

@@

\section[Summary of problems]{Summary of Proposed Problems}
\label{sec:myresearchintro}
In Section~\ref{sec:motive} we see that consecutive-ones property and
its equivalent problem of interval labeling of a hypergraph is a
special case of the general problem of tree path labeling of path
hypergraphs.  The problem of consecutive-ones property testing can be
easily seen as a simple constraint satisfaction problem involving a
hypergraph or a system of sets from a universe. Every column (row) of
the binary matrix can be converted into a set of non-negative integers
which are the indices of the rows (columns) with {\un}s in that column
(row). When observed in this context, if the matrix has the COP on
columns (rows), a reordering of its rows (columns) will result in sets
that have only consecutive integers. In other words, the sets after
applying the COP row (column) permutation are intervals.  In this
form, one can see that this is indeed the problem of finding interval
assignments to the given set system \cite{nsnrs09} with a single
permutation of the universe (set of row or column indices for COP of
columns or rows, respectively) which permutes each set to an
interval. The result in \cite{nsnrs09} characterizes interval
assignments to the sets which can be obtained from a single
permutation of the universe. The cardinality of the interval
assigned to it must be same as the cardinality of the set, and the
intersection cardinality of any two sets must be same as the
intersection cardinality of the corresponding intervals. This is a
necessary and sufficient condition. \tnote{(ICPIA) put reference to
  survey chapter}

@@

\section[Preliminaries]{Preliminaries to new results}
\label{ch:prelims}

@@

\section[Characterization of FTPL]{Characterization of Feasible Tree Path Labeling}
\label{sec:feasible}

@@

\section[Special target trees]{ Computing feasible TPL with special target trees}
\label{sec:spltargettree}

@@

\section[Complexity]{Complexity of Tree Path Assignment-A Discussion}
\label{complexity}
Recall that the input to the Tree Path Assignment question is an order
pair $(\cF,T)$ where $\cF$ is a family of subsets of an universe $U$,
and $T$ is a tree such that $|V(T)| = |U|$.  The question is to come
up with a bijection from $U$ to $V(T)$ such that the image of each set
in $\cF$ is a path in $T$.
